---
title: "newtables"
author: "Your Name"
date: "2023-04-14"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Introduction

```{r}

library(table1)

library(table1)
library(magrittr)
library("flextable")
df=readRDS("output/amit_df_bp.rds")
dat=df

dffhs=readRDS("output/fh_full.rds")

select=dat[which(dat$prscat=="low"),c("choladj","sbp","enroll_age")]

meanCIfunct=function(select)
  {
  sapply(1:ncol(select),function(i){
  n=names(select)[i]
  print(n)
  x=select[,get(n)]
  names(select)[i]
 mean_x <- mean(x)
ci_x <- t.test(x)$conf.int

# Print the results
cat("Mean:", round(mean_x, 2), "\n")
cat("95% CI:", round(ci_x[1], 2), "-", round(ci_x[2], 2), "\n")
  })}

select=dat[which(dat$prscat=="high"),c("choladj","sbp","enroll_age")]
meanCIfunct(select)

summary(select)

select=dat[which(dat$prscat=="low"),c("choladj","sbp","enroll_age")]
meanCIfunct(select)

summary(select)

summary(dat$phenos.CAD_censor_age[dat$phenos.has_CAD==1&dat$prscat=="high"])

summary(dat$phenos.CAD_censor_age[dat$phenos.has_CAD==1&dat$ascvdcat_all=="high"])
summary(dat$phenos.enrollment[dat$ascvdcat_all=="high"])

mean(dat[which(phenos.enrollment<65&phenos.enrollment>55&prs.r<0.02),phenos.has_CAD==1])

mean(dat[which(phenos.enrollment<65&phenos.enrollment>55&prs.r>0.98),phenos.has_CAD==1])

```

# Abstract numbers
 Among those <55 years, CAD PRS predicted 3.5-fold more events than PCE alone, including XXX-fold for events occurring prior to XXX years, with delta AUC of XXX (95% XXX-XXX).

```{r}

sum(df$phenos.enrollment<45&df$phenos.has_CAD==1)
sum(df$phenos.enrollment<45&df$phenos.has_CAD==1&df$prs.r>0.80&df$ascvd_10y_accaha_all<7.5)
138
sum(df$phenos.enrollment<45&df$phenos.has_CAD==1&df$ascvd_10y_accaha_all>7.5&df$prs.r<0.80)
44

sum(df$phenos.enrollment<45&df$phenos.has_CAD==1&df$prs.r>0.80&df$ascvd_10y_accaha_all<7.5&df$phenos.CAD_censor_age<60)
138

sum(df$phenos.enrollment<45&df$phenos.has_CAD==1&df$ascvd_10y_accaha_all>7.5&df$prs.r<0.80&df$phenos.CAD_censor_age<60)
44

````

 
 For those >55y, CAD PRS only identified XXX-fold more events than PCE alone with delta AUC XXX (95% XXX-XXX).
 
```{r}
sum(df$phenos.enrollment>55&df$phenos.has_CAD==1&df$prs.r>0.80&df$ascvd_10y_accaha_all<7.5)

sum(df$phenos.enrollment>55&df$phenos.has_CAD==1&df$ascvd_10y_accaha_all>7.5&df$prs.r<0.80)
```



#mean age of CAD event in high vs. low risk was 2.9 years earlier for genomic risk and 13.7 years later for clinical risk. Among people <55 years, addition of PRS augmented the C-statistic of a clinical model by 6.3% (95% CI 4.8-7.8). 


###Delta AUC

```{r}
source("code/utils.R")
library(ggplot2)

df=readRDS("output/amit_df.rds")

df$prscat <- cut(df$prs.r, breaks=c(0, 0.20,0.80,1), labels=c("low", "intermediate","high"))
set.seed(456)

  #which(df$phenos.enrollment>ages[i]&df$phenos.enrollment<ages[i+1])
  d=df[df$phenos.enrollment<55,]
  
  indices=sample(nrow(d))
  
  d_train=d[indices[1:(length(indices)/2)],]
  d_test=d[indices[(length(indices)/2+1):length(indices)],]
  model_glm = glm(phenos.has_CAD  ~ prscat, data = d_train, family = "binomial")
  
  test_prob = predict(model_glm, newdata = d_test, type = "response")
  test_roc = roc(d_test$phenos.has_CAD~ test_prob, plot = F)
  prs.roc=test_roc$auc
  s.prs=sqrt(var(test_roc))
  
  
  ### for pce and prs
  model_glm = glm(phenos.has_CAD  ~ ascvdcat_all+prscat, data = d_train, family = "binomial")
  
  test_prob = predict(model_glm, newdata = d_test, type = "response")
  test_roc = roc(d_test$phenos.has_CAD~ test_prob,plot=F)
  pce.prs.roc=test_roc$auc
  
    ### for pce only
  model_glm = glm(phenos.has_CAD  ~ ascvdcat_all, data = d_train, family = "binomial")
  
  test_prob = predict(model_glm, newdata = d_test, type = "response")
  test_roc = roc(d_test$phenos.has_CAD~ test_prob,plot=F)
  pce.roc=test_roc$auc
  
  pce.prs.roc-pce.roc
  
roc.test(pce.prs.roc,pce.roc)
  
  
  
  
  =sqrt(var(test_roc))
  
  delta.auc=pce.roc-prs.roc
  se=sqrt(s.pce^2+s.prs^2)
  df=dim(d)[1]+dim(d)[1]-2
  
  
  delta.auc+se
  delta.auc-se
  
```



  
1) Calculate the difference in AUC between the two models (AUC1 - AUC2).

Calculate the standard error of the difference using the following formula:

SE = sqrt(SE1^2 + SE2^2), where SE1 and SE2 are the standard errors of AUC1 and AUC2, respectively.

Calculate the degrees of freedom (df) using the following formula:

df = n1 + n2 - 2, where n1 and n2 are the sample sizes for the two models.

Calculate the t-statistic using the following formula:

t = (AUC1 - AUC2) / SE

Find the p-value associated with the t-statistic using a t-distribution with df degrees of freedom.

Use the p-value to find the confidence interval for the difference in AUC. For example, a 95% confidence interval can be calculated as:

AUC1 - AUC2 ± t_crit * SE

where t_crit is the critical t-value for a 95% confidence level and df degrees of freedom. The critical t-value can be found using a t-distribution table or a statistical software package.
(prs.roc-pce.roc)+1.96*(s.prs-s.pce)
(prs.roc-pce.roc)-1.96*(s.prs-s.pce)


```{r}

Among participants in the bottom decile of PRS, XX CAD events occurred at mean age XX (95% CI  XX-XX) years, and there was a steady decrease in the mean age of CAD events by PRS decile, with XX events occurring at mean age XX (95% CI  XX-XX) years among participants in the top decile of PRS. Conversely for PCE, the mean age of event was lowest in the bottom decile – XX events occurring at mean age XX (95% CI XX-XX) years – and highest in the top decile of PCE – XX events occurring at mean age XX (95% CI XX-XX) years.  PRS: Polygenic Risk Score, PCE: Pooled Cohort Equations


##
#df = readRDS("output/amit_df.rds")
df = readRDS("output/amit_df_with_pc_correction.rds")
# ## make sure normalized
df$prs_quant = scale(df$scaled_score)
df$prs.r = (rank(df$prs_quant) / length(df$prs_quant))
# 
prs.dec=df%>%group_by(round(prs.r,1))%>%summarise(m=mean(phenos.CAD_censor_age[phenos.has_CAD==1]),se=sd(phenos.CAD_censor_age[phenos.has_CAD==1])/sqrt(sum(phenos.has_CAD==1)),s=sum(phenos.has_CAD==1))

prs.dec$upper=prs.dec$m+1.96*prs.dec$se
prs.dec$lower=prs.dec$m-1.96*prs.dec$se



pce.dec=df%>%group_by(round(ascvd.r,1))%>%summarise(m=mean(phenos.CAD_censor_age[phenos.has_CAD==1]),se=sd(phenos.CAD_censor_age[phenos.has_CAD==1])/sqrt(sum(phenos.has_CAD==1)),s=sum(phenos.has_CAD==1))

pce.dec$upper=pce.dec$m+1.96*pce.dec$se
pce.dec$lower=pce.dec$m-1.96*pce.dec$se
```


